### 2016-07-26 sections/image_texts/all.tex
After-submission

\begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and26.png}
    \caption{Two dimensional SOM of M31 using $10\times10$ grid. Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, The hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
    \label{fig: all_derived_ones}
\end{figure}

>>>>

\begin{figure}
        \centering
        \includegraphics[width=0.5\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and26.png}
    \caption{Two dimensional SOM of M31 using $10\times10$ grid. Similar to Figs.\ref{fig: sample} and \ref{fig: M31_nets_1d}, the hexagonal shapes show the neurons and the grey cycle colours between neurons show the differences between weight of each neuron.}
    \label{fig: all_derived_ones}
\end{figure}

### 2016-07-26 sections/image_texts/col3byall.tex
After-submission

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}

@@

        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}

@@

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}

>>>>

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission }

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission }

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission }

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission }

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
         \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{{\mathrm Dust}}$}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
          \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{{\mathrm Dust}}$}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR(FUV\ +\ 24\ $\mu$m)}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{{\mathrm Stars}}$}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{{\mathrm TIR}}$}

@@

        \includegraphics[width=54mm, height=37mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{{\mathrm Total\ gas}}$}

@@

        \includegraphics[width=54mm, height=37mm ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and RHI.}

@@

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as the order of data in Fig.~\ref{fig: cor_cluster1}.}
